Hierarchy Builder

### 2020-04-27 coqws/easychair.tex

For space constraints we omit the declaration
of the green arrows in Fig.~\ref{fig:hierarchy} which are alternative interfaces
called factories. They provide specialized interfaces to
build structures for others.
Factories are used to accommodate the insertion of
intermediate structures in a hierarchy without breaking user code, as we all
as to implement shortcuts: the factory to build a \coq{Ring} from \coq{Type}
(rightmost green arrow)
can omit the commutativity axiom of the addition, since it is implied
by the other axioms~\cite{nearrings}.
\bibliography{biblio}

>>>>

For space constraints we omit the declaration
of the green arrows in Figure~\ref{fig:hierarchy} which are alternative interfaces
called factories. They provide specialized interfaces to
build structures from others.
Factories are used to accommodate the insertion of
intermediate structures in a hierarchy without breaking user code, as well
as to implement shortcuts: e.g. the factory to build a \coq{Ring} from a \coq{Type}
(rightmost green arrow)
can omit the commutativity axiom of the addition, since it is implied
by the other axioms~\cite{nearrings}.
\bibliography{biblio}
